Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2017-02-06 paper.tex
modifiche parte MKL e algoritmo - ora numero pagine corretto!

\subsection{Multiple Kernel Learning}
\label{MKL}
MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014}. % Zien2007,Wang2015a,Sun
The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ with a constraint in the form:
$
	H_R^q = \{ \xx \mapsto \textbf{w} \cdot \pphi_\KK(\xx) : \KK = \sum_{r=1}^R \eta_r \KK_r, \mmu \in \Psi_q, \|\textbf{w}\|_2 \leqslant 1 \}
$
with $\Psi_q = \{ \mmu : \mmu \succcurlyeq 0, \| \mmu \|_q = 1 \}$ and considering the function $\pphi_\KK$ as the feature mapping from the input space to the feature space. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.

Using this formulation, we are studying the family of sums of kernels in the feature space. It is well know that the sum of two kernels can be seen as the concatenation of the features contained in both the RKHS \cite{Shawe-Taylor2004}. Extending the same idea, the weighted sum of a list of basic kernels can be seen as a weighted concatenation of all the features contained in all the RKHS (where the weights are the square roots of the learned weights $\eta_k$).

@@

\section{Proposed framework}
Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be high. Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
In order to avoid these problems, we propose a method to reduce the number of kernels to compute on the complete dataset, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.\\
In particular if $\boldsymbol{\eta}$, the combination vector learned using the whole set of data and all kernel functions, is similar to the weights vector $\hat{\boldsymbol{\eta}}$ learned using the same kernels calculated on a subset of data, we can compute just $\hat{\boldsymbol{\eta}}$ .
%In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
Moreover, we can use the values in $\hat{\boldsymbol{\eta}}$ to perform a ranking over kernels, removing those below a (user-specified) threshold.
Then we compute the kernel matrix, on all the available data, for just the top kernels, and fit a model combining them.

@@

\begin{lstlisting}
Input: training matrix (*$\XX$*), list of kernel functions (*$L$*)
(*$\XXs$*) (*$\leftarrow$*) subset_of((*$\XX$*))
(*$KL_\textsc{s}$*) (*$\leftarrow$*) [ker_fun((*$\XXs$*)) for ker_fun in (*$L$*)] #calculate matrices on (*$\XXs$*)
(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$KL_\textsc{s}$*)) #calculate weights
(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}$*)) #get the top functions
(*$KL$*) (*$\leftarrow$*) [ker_fun((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #calculate top matrices on (*$\XX$*)
\end{lstlisting}

@@

We have presented an efficient approach to model selection for graph kernels
based on the multiple kernel learning framework. We have shown how working on
small subsets (up to 10\%) of the data yields results that are stable and
accurate enough to select the optimal combination of kernels via EasyMKL.
We have investigated three methods to efficiently combine a subset of
kernels while preserving at the same time an high AUC score for the downstream
machine learning algorithms. Finally, we showed how we can use the simple
summation of the selected kernels, avoiding the expensive step of running MKL
on the full training set, to scale the MKL approach to very large
datasets.

In future work we will extend the library of graph kernels to obtain a
comprehensive and easy to use software package.

>>>>

\subsection{Multiple Kernel Learning}
\label{MKL}
MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014}. % Zien2007,Wang2015a,Sun
The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ in the form:
$ \KK = \sum_{r=1}^R \eta_r \KK_r$ with $\eeta \in \Psi_q = \{ \eeta : \eeta \succcurlyeq 0, \| \eeta \|_q = 1 \}$. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.

Using this formulation, we are studying the family of sums of kernels in the feature space and it is well know that the sum of two kernels can be seen as the concatenation of the features contained in both the RKHS \cite{Shawe-Taylor2004}. Extending the same idea, the weighted sum of a list of basic kernels can be seen as a weighted concatenation of all the features contained in all the RKHS (where the weights are the square roots of the learned weights in the vector $\eeta$).

@@

\section{Proposed framework}
Often, to work well MKL algorithms require an high number of kernels, and when we use structured data as input, such as graphs, the computational effort to calculate each of them can be high. Moreover each kernel requires an amount of memory that depends on the number of samples, making the MKL approach unpractical when the number of samples and the number of kernels are huge.
In order to avoid these problems, we propose a method to reduce the number of kernels to compute on the complete dataset, based on the robustness of the combination vector $\boldsymbol{\eta}$ when considering just a subset of the available data.\\
In particular if the combination vector learned using the whole set of data and all kernel functions $\boldsymbol{\eta}$ is similar to the weights vector $\hat{\boldsymbol{\eta}}$ learned using the same kernels calculated on a subset of data, we can compute just $\hat{\boldsymbol{\eta}}$ .
%In this way we can learn quickly the kernels combination, but we have to calculate all kernels anyway.
Moreover, we can use the values in $\hat{\boldsymbol{\eta}}$ to perform a ranking over kernels, removing those below a (user-specified) threshold.
Then we compute the kernel matrix, on all the available data, for just the top kernels, and fit a model combining them.

@@

\begin{lstlisting}
Input: training matrix (*$\XX$*), list of kernel functions (*$L$*)
(*$\XXs$*) (*$\leftarrow$*) subset_of((*$\XX$*))
(*$K_\textsc{s}$*) (*$\leftarrow$*) [ker_funct((*$\XXs$*)) for ker_funct in (*$L$*)] #matrices on (*$\XXs$*)
(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$K_\textsc{s}$*)) #weights of the functions in L
(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}$*)) #get the top functions
(*$KL$*) (*$\leftarrow$*) [ker_funct((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #top matrices on (*$\XX$*)
\end{lstlisting}

@@

We have presented an efficient approach to model selection for graph kernels
based on the multiple kernel learning framework. We have shown how working on
small subsets (up to 10\%) of the data yields results that are stable and
accurate enough to select the optimal combination of kernels via EasyMKL.
We have investigated three methods to efficiently combine a subset of
kernels while preserving at the same time an high AUC score for the downstream
machine learning algorithms. Finally, we showed how we can use the simple
summation of the selected kernels, avoiding the expensive step of running MKL
on the full training set, to scale the MKL approach to very large
datasets.
In future work we will extend the library of graph kernels to obtain a
comprehensive and easy to use software package.
